\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=.9in]{geometry}

\titleformat{\section}
{\huge\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries\Large}
{\hspace{-.10in}}
{0em}
{}

\titleformat{\subsubsection}
{\bfseries}
{}
{0em}
{}[———————————]

\renewcommand{\maketitle}{
\begin{flushright}
{\huge\bfseries
\theauthor}

\vspace{.25em}
Pittsburgh, PA

\vspace{.25em}
johnlradford23@gmail.com

\vspace{.25em}
https://johnlradford.io 

\end{flushright}
}

\begin{document}

\title{R\'esum\'e}
\author{John L. Radford}

\maketitle

\section{Overview}

I've spent four+ years working as an IT support technician, all the while
building skills in web/Email hosting, domain registration, scripting, testing,
automation, as well as front and backend web development. I'm now interested in
breaking into the software development field. As a computer nerd and home Linux
user, I enjoy spending my nights writing useful tools (as well as some trivial
pieces of software) for myself, my friends, and my coworkers. So I figure might
as well try to get paid for it!

\section{Technical Skills}

\subsection{Languages}

\subsubsection{Programming Languages}

C, Bash, Perl, PHP, Python, SQL

\subsubsection{Markup Languages}

HTML, Markdown, {\LaTeX}, Mediawiki Markdown

\subsection{Web Frameworks}

Flask, CGI, Bootstrap

\subsection{CMSs}

WordPress, MediaWiki

\subsection{Operating Systems}

FreeBSD, Linux

\subsection{Server Technologies}

Apache, Nginx, Postfix, Dovecot, MySQL

\subsection{Virtualization / Containerization}

Docker, QEMU/KVM, VirtualBox

\subsection{Misc}

Editor: Vim, Shell: Bash, Version Control: Git

\section{General Skills}

\subsection{Leadership Experiences}

\begin{itemize}
\item Eagle Scout - Troop 66

\item Ex Pluribus Capitibus Supra of the UPG Campus Alliance for Free Thought

\item President of University of Pittsburgh's delegation to the model European Union (2016)
\end{itemize}

\subsection{Communication Experience}

\begin{itemize}
\item As a student, I have written hundreds of academic papers for a wide variety 
of courses, on subjects ranging from International Relations to Medieval English 
literature.

\item As a support technician, I have responded to thousands of customer Emails about 
technical and bureaucratic subjects with people from all around the globe.

\item As a coworker, I've effectively communicated with colleagues \& team members, 
both in person and via messaging applications, to diagnose and resolve technical 
issues on the fly.

\item As a family member who knows something about computers (as well as in my
job as a support technicain), I am used to providing live troubleshooting and technical 
support over the phone (24/7).
\end{itemize}

\subsection{Creativity / Problem Solving}

\begin{itemize}
\item As a tinkerer and home computer enthusiast I enjoy building custom internal
solutions for my home network / server rack.

\item As a web design enthusiast I enjoy building good looking and useful web
applications that work well on the front and backend.

\item As an amateur hacker and script kiddy I enjoy finding interesting ways 
around technical restrictions, as well as ways to make software more secure to begin 
with.
\end{itemize}

\section{Education}

\textbf{University of Pittsburgh - Greensburg Campus}

\begin{itemize}
\item Graduated: 2017

\item Major: Humanities Gen., Philosophy/Art History/Classical Literature

\item Minor: Political Science

\item Related Coursework: Technical Writing Classes, General Written and Professional
Communication Experience, Courses in Math, Public Speaking, Rhetoric, Logic,
and Heuristics.
\end{itemize}

\section{Work Experience}

\subsection{IT Helpdesk Assistant -- University of Pittsburgh Greensburg}

\textbf{Timeframe: Sprint \& Fall Semester 2017}

I worked as a workstudy for the University of Pittsburgh at Greensburg where I
was responsible for assisting students and faculty with computing issues, both
in person and over the phone. I learned to work with networking, printing, and
AV equipment. Learned to resolve issues on Mac, Windows, and mobile platforms.

\subsection{Customer Support Technician -- Pair Networks, Inc.}

\textbf{Timeframe: 2018 - Present}

I currently work as an overnight support technician (level 2) for a web hosting
company on Pittsburgh's southside. My duties involve, answering the phone at
2am because someone accidentally deleted a WordPress plugin, helping old ladies
setup their Email clients, kindly doing the needful for our overseas customers,
blocking RU \& CN IPs by the 0/24, trying to get MySQL to restart, failing,
tailing the error log, rebooting, fscking my life away, all the while
delivering a satisfying customer service experience.

\subsubsection{Departments \& Teams} 

\noindent
\textbf{General Support Department}

The general support department is the foremost front facing customer interface
for the company. General support staff are responsible for responding to
tickets via Email and answering incoming phone calls. The type of issues
handled by this team are very broad, however they typically include; providing
configuration assistance for Apache and PHP, diagnosing DNS issues, providing
connection assistance for FTP/SSH/IMAP/POP3/SMTP, providing help with domain
registration services, help importing/exporting SQL databases, basic site
optimization assistance, ect..

\vspace{.25em}
\noindent
\textbf{Urgent Bolt  Live Server Monitoring Team}

The urgent bold (UB) aka live server monitoring team is responsible for
watching the Icinga monitoring interface and responding to outages and alerts
as they occur. A prototypical example is having to respond to a load spike
caused by excessive malign traffic toward a poorly coded web application. This
is typically resolved by identifying and then firewalling the bad actors
responsible for the traffic in order to return the server to stability.

UB team members are also responsible for responding to and diagnosing the
source of large accumulations of Email, typically caused by spammers
manipulating web forms or compromising mailboxes.

Lastly, UB members are responsible for, emergency drive / hardware
replacements, emergency reboots, emergency escalations, and answering the
doorbell.

\vspace{.5em}
\noindent
\textbf{Upgrade \& Moves Department}

At Pair, the upgrade \& moves department is responsible for moving customer
accounts between various generations of hosting platforms and account types.

I have moved thousands of accounts, websites, mailboxes, databases, DNS zone
files, all sort of configs, etc. between various generation FreeBSD and Linux
servers as part of the upgrades and moves team.

\vspace{.5em}
\noindent
\textbf{Signups Fraud Detection Team}

The signup and fraud detection team is responsible for manually reviewing the
signup data of recently created accounts that have been flaged by the automated
fraud detection systems. We check for inconsistencies between for example; the
signup's business address and signup's IP address location, as well as checking
for other signs for fraud.

\vspace{.5em}
\noindent
\textbf{Unofficial Scripting}

In certain ways the culture of my job is very \emph{work your own way} as long
as you get the same results as the rest of us. Everybody there has their own
shell aliases and custom scripts.

Working overnight I have an abundance of free time. My nightly life now
consists of about 30\% doing my job and about 50\% writing tools to make my job
easier (the last 20\% is youtube). I work in an information rich environment
that is desperately in need of automation and I enjoy writing tools to help
improve my life and the lives of my coworkers.

\vfill

\begin{tabular}{r}
\small\today\\
\end{tabular}

\begin{center}
John R. -- Resume 
\end{center}

\end{document}
